Context Aware Virtual Assistant with Case-Based Conflict Resolution in Multi-User Smart Home Environment

### 2018-01-09 Paper/Paper.tex
Deleted old CBR. Updated Wiki page.

    \author{Bauyrzhan Ospan\inst{1} \and Kenzhegali Nurgaliyev\inst{1} \and Mario Jose Quinde Li Say Tan \inst{2} \and Nawaz Khan \inst{2}}
    \institute{Department of Information Technology, Kazakh University of Technology and Business, Kayim Muhamedhanov 37A, Astana 010000, Kazakhstan \\ \email{{bospan,knurgaliev}@gmail.com}
    \and Department of Computer Science, Middlesex University, The Burroughs, London NW4 4BT, United Kingdom \\ \email{{MQ093,N.X.Khan}@live.mdx.ac.uk}}

@@

        Smart Home, Case-Based Reasoning, Context Awareness, Multiple User systems, Virtual Assistant

@@

    \section{Sequences}
    %
    \section{Results and Validation}
    %
    \section{Conclution}
    \section{References}
    \begin{thebibliography}{1}
        \bibitem {1}
        Alirezaie, M., Renoux, J., Köckemann, U., Kristoffersson, A., Karlsson, L., Blomqvist, E., Tsiftes, N., Voigt, T., Loutfi, A.: An Ontology-based Context-aware System for Smart Homes: E-care@home. Sensors. 17, 1586 (2017).

>>>>

    \author{Bauyrzhan Ospan\inst{1} \and Nawaz Khan \inst{2} \and Juan Augusto \inst{2} \and Mario Jose Quinde Li Say Tan \inst{2} \and Kenzhegali Nurgaliyev \inst{1}}
    \institute{Department of Information Technology, Kazakh University of Technology and Business, Kayim Muhamedhanov 37A, Astana 010000, Kazakhstan \\ \email{{bospan,knurgaliev}@nu.edu.kz}
    \and Department of Computer Science, Middlesex University, The Burroughs, London NW4 4BT, United Kingdom \\ \email{{N.X.Khan,J.Augusto,MQ093}@live.mdx.ac.uk}}

@@

        Case-Based Reasoning, Context Awareness, Multiple User systems, Smart Home, Virtual Assistant

@@

    Case-Based Reasoner works by finding the lowest distance of input case to the cases inside the database.
    CBR is an artificial intelligence approach to determine a similarity amongst a set of cases.
    This method indexes cases from history of the system usage and retrieves best similar case by measurement of distance between the input case and past cases.
    The result of finding best match is stored inside the cases database to update the cases database and adapt old solution to the new variables and environment.
    CBR is based on a suggestion that the similar cases have similar solution.
    The decisions in our system is binary (0 for not change device status, 1 for change it).
    As a result, it is accessible that CBR assumption works in our system.
    Most of the CBR systems uses k-nearest neighbour algorithm.
    The accuracy of this classification algorithm seriously depends on the metrics or system of measurement used to compute distances between different cases.
    The nearest neighbour algorithm determines the similarity or dissimilarity of a new case with the case base and follows a cyclical process of Retrieve-Reuse-Revise-Retain.
    In our case inputs to the system are in different system of measurements.
    Cases in the system are build on preferences and priority of users of the system.
    Both two variables have different basis.
    As a result, standard Euclidean Distance cannot be used as a distance measurement algorithm.
    It was proposed to use Mahalanobis distance that is the global linear transformation tool of the input spaces of the cases from different classes separated by a large margins.
    Using of Mahalanobis distance significantly increases kNN accuracy.
    In addition, there was used a Genetic Algorithm to find best value of Mahalanobis covariance matrix.
    It is was set nearly 11 quadrillion types of mutations patterns.
    The covariance matrix was used as genome of each genome in the epoch.
    As a result, each epoch system chooses best accuracy model and mutates it`s one hundred children with different not significant mutations in the genome.
    Then the system iterate again while accuracy of the best model (king) will not reach threshold value.
    \subsection{Device Control Unit}
    Smart Home environment of the Farm Side Middlesex University is driven by Vera Secure system.
    In consequence, we developed API to communicate with it.
    Vera Secure system has own web interface.
    In order to communicate with it, we sending and receiving GET and POST requests.
    Special POST requests changes status of the devices, which are kettle and light in our experiment.
    Next, updating information about device statuses is done by parsing response from special GET request sent to the Vera Secure server.
    \section{Sequences}
    Sequences inside the system are mentioned in this chapter.
    \subsection{Terminology}
    We used user types and preference system proposed by \cite{9} .
    As a result, different group of users were outlined and divided by age.
    Moreover, we declared updated system of preferences.
    \begin{table}
        \caption{List of users and preferences}
        \begin{tabular}{llllll}
            \hline\noalign{\smallskip}
            User types & Preferences (positions 0,1,2,3,4,5)\\
            \noalign{\smallskip}
            \hline
            \noalign{\smallskip}
            Adult (26-69 ages) & Security, Health, Work, Food, Energy, Entertainment\\
            Elderly (older 70) & Health, Security, Food, Energy, Entertainment, Work\\
            Young (up to 25 ages) & Security, Work, Entertainment, Health, Food, Energy\\
            \hline
        \end{tabular}
    \end{table}

    \subsection{Regular Case}
    \subsection{Conflicting Case}
    \section{Results and Validation}
    %
    \section{Conclution}
    \section{References}
    \begin{thebibliography}{1}
        \bibitem {1}
        Alirezaie, M., Renoux, J., Köckemann, U., Kristoffersson, A., Karlsson, L., Blomqvist, E., Tsiftes, N., Voigt, T., Loutfi, A.: An Ontology-based Context-aware System for Smart Homes: E-care@home. Sensors. 17, 1586 (2017).
